\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{soul}
\usepackage{xcolor}
\usepackage{marvosym}
\usepackage{fontspec} %for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} %other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{longtable} % for longtable environment

% Use o pacote geometry para controlar as margens
\usepackage[left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}

% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} %for Grades
\usepackage{titlesec} %custom \section
\usepackage{multicol}

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\usepackage[T1]{fontenc}
\usepackage[scaled]{helvet}
\renewcommand*{\familydefault}{\sfdefault}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1pt}{3pt}

\hyphenation{im-pre-se}

\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.95\paperheight}
\setlength{\parindent}{0pt}

\begin{document}

\pagestyle{empty} % sem número de páginas

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge Maicon Kevyn Moraes
		}\vspace{0.1cm}\\AI Engineer | GenAI Engineer\\{\color{gray}}\bigskip\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
\section{Personal data}

\begin{tabular}{rl}
    {Email:}     & osonodenewton@gmail.com \\
    {LinkedIn:} & \href{https://www.linkedin.com/in/maiconkevyn/}{linkedin.com/in/maiconkevyn/} \\
    {Portifolio:} &
    \href{https://maicon-kevyn-portifolio.vercel.app/}{maicon-kevyn-portifolio}  \\
    {Phone:} & \href{}{+55 51993205204}

\end{tabular}

\section{Education}
\begin{tabular}{r|p{11cm}}
 \textbf{ 2021/1 - 2026/1}& \textbf{Bachelor's Degree in Astrophysics, \href{http://www.ufrgs.br/english/home}{Federal University of Rio Grande do Sul – UFRGS} }\\

\textbf{ 2023/1 - Nov/2025}& \textbf{Undergraduate Degree in Data Science, \href{https://www.uninter.com/}{International University Center – UNINTER} }\\

\textbf{2026/1 - 2028/1} & \textbf{Master's Degree in Data Science and Artificial Intelligence, \href{https://www.pucrs.br/}{Pontifical Catholic University of Rio Grande do Sul (PUCRS)}} \\



 \end{tabular}

\section{Summary}
AI Engineer with experience building and shipping LLM-based products, retrieval systems, and document extraction pipelines. I work across the practical side of applied AI, from prompts and evaluation to APIs and cloud infrastructure, mainly on AWS and Databricks. Built retrieval systems for 500+ documents with 92\% precision, set up automated evaluation with MLflow LLM-as-a-Judge, and developed serverless pipelines with Lambda, Step Functions, SageMaker, S3, and DynamoDB. I also have a solid background in classical machine learning, including scikit-learn and XGBoost, which helps me move comfortably between traditional ML and modern GenAI work.

\section{Core Skills}
\textbf{Generative AI:} LLM applications, RAG, vector search, tool calling, prompt engineering, prompt evaluation, LangChain, LangGraph, Ragas, structured extraction workflows \\
\textbf{Machine Learning:} Scikit-learn, XGBoost, LLM fine-tuning, experiment tracking, model evaluation \\
\textbf{Backend \& APIs:} Flask, REST APIs, API integration, Pydantic \\
\textbf{Cloud \& MLOps:} AWS (Lambda, S3, Step Functions, SageMaker, API Gateway, ECR), Docker, Jenkins, Git, Promptfoo \\
\textbf{Data Platform:} Databricks, PySpark, MLflow, Lakeflow, ETL/ELT pipelines \\
\textbf{Databases:} PostgreSQL, pgvector, SQLite, DynamoDB, Pinecone \\
\textbf{Programming:} Python, SQL \\
\textbf{Visualization:} Databricks Dashboards, Streamlit \\
\textbf{Languages:} English - Intermediate (B2), Portuguese (Native), Spanish - Elementary (A2)



\begin{longtable}{p{0.18\textwidth}|p{0.74\textwidth}}

\textbf{Nov/2024 - Present} &
\textbf{\large Data Scientist | AI Engineer at ADP} \par
$\bullet$ Built end-to-end RAG pipelines with LLMs, including document parsing with AWS Textract, PyMuPDF, and docling, prompt design, vector indexing, and hybrid search in AWS OpenSearch.\par

\vspace{1.3pt}


$\bullet$ Designed structured extraction pipelines for payroll documents using prompt design, tool calling, and schema-based outputs, with AWS Lambda, Step Functions, S3, API Gateway, and DynamoDB supporting orchestration and downstream integrations.\par


\vspace{1.3pt}

$\bullet$ Delivered a RAG pipeline on Databricks Vector Search for 500+ employee benefits documents, reaching 92\% retrieval precision and reducing query response time by 60\%.

\vspace{1.3pt}

$\bullet$ Implemented MLflow LLM-as-a-Judge evaluation to automate quality checks and reduce manual review of LLM outputs.\par
\vspace{1.3pt}

$\bullet$ Improved prompt quality with Promptfoo and PromptFlow, combining automatic metrics with model-based evaluation to compare relevance, quality, and consistency at scale.\par


\vspace{1.3pt}

$\bullet$ Fine-tuned LLMs on Databricks with experiment tracking in MLflow, then deployed them on AWS SageMaker with custom Docker images and integrated them with Lambda, S3, and Step Functions.\par

\vspace{1.3pt}

$\bullet$ Optimization of classification pipelines with pandas, scikit-learn, and XGBoost, implementing hyperparameter tuning and preprocessing strategies for performance gains.\par

\vspace{1.3pt}

\\[4pt]

\textbf{Jan/2025 -- Present} &
\textbf{\large Data Science Researcher in Artificial Intelligence at PUCRS} \par
$\bullet$ Built a LangGraph-based text-to-SQL agent connected to PostgreSQL to answer natural language questions about data from the Brazilian Unified Health System (SUS), along with a web interface for end users.

$\bullet$ Designed and implemented the PostgreSQL database schema, modeling 15+ tables with proper normalization, indexing strategies, and foreign key constraints to ensure query performance and data integrity for 11M+ health records.\\[2pt]


\\[4pt]

\textbf{Feb/2024 -- Nov/2024} &
\textbf{\large Data Scientist Intern at ADP} \par
$\bullet$ Benchmarking of LLMs (OpenAI and Hugging Face) applied to sentiment analysis and topic modeling, with implementation of an interactive dashboard to monitor sentiment metrics by topic.\par

$\bullet$ Unsupervised clustering of feedback to uncover recurring themes and audience profiles using LLM-based embeddings and algorithms such as K-Means and HDBSCAN; applied dimensionality reduction for interpretability (UMAP) and validated cluster quality (silhouette/Davies–Bouldin), integrating insights into the sentiment/topic monitoring workflow.


\\[4pt]

\textbf{Feb/2022 -- Aug/2022} &
\textbf{\large Data Engineer Intern at Lojas Renner SA} \par
$\bullet$ Processing and optimization of large data volumes with PySpark on Azure Databricks, applying the medallion architecture (silver/gold layers) and building pipelines with Azure Data Factory.

$\bullet$ Designed a medallion layer and built end-to-end pipelines in a retail context to deliver optimized, BI-ready tables for analytics teams.
\\[4pt]


\textbf{Aug/2021 -- Jan/2024} &
\textbf{\large Data Science Researcher at Astronomy Department at UFRGS} \par
$\bullet$ Python and SQL for extraction, cleaning, and preprocessing of large SDSS astronomical datasets.\par
$\bullet$ Machine learning models (Random Forest, SVM, Gradient Boosting) for galaxy classification using morphological and photometric features.\par
$\bullet$ Supervised models to predict galaxy quiescence from stellar parameters (mass, velocity dispersion, spectral indices).
\\

\end{longtable}

% {\footnotesize
% \titleformat{\section}{\normalsize\scshape\raggedright}{}{0em}{} % redefine só aqui

% \begin{multicols}{3}

% \section{Languages}
% Portuguese {\color{gray}(Native)}\\
% English {\color{gray}(Intermediate - B2)}\\
% Spanish {\color{gray}(Conversational - A2)}
% \columnbreak

% \section{Technical skills}
% Python, SQL, Databricks, Git, AWS
% % $\bullet$ SQL \\
% % $\bullet$ Databricks \\
% % $\bullet$ Git \\
% \columnbreak

% \section{General skills}
% Quick learning, Self-Taught, Effective team-working

% \end{multicols}

}

%\newpage
%\hypertarget{gmat}{\textsc{Gmat}\setmainfont{LMRoman10 Regular}\textregistered\setmainfont[SmallCapsFont=Fontin-SmallCaps]{Fontin-Regular}}

%\XeTeXpdffile ''GMAT.pdf'' page 1 scaled 800


\end{document}

